### 2018-05-11 README.Rmd
Add netlify link
Tweak header on pkgdown site

To install the developmental version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this developmental version is at https://infer.netlify.com.

@@

We welcome others helping us make this package as user friendly and efficient as possible. Please review
our [contributing](https://github.com/andrewpbray/infer/blob/develop/CONDUCT.md) and [conduct](CONDUCT.md) guidelines. Of particular interest is
helping us to write `testthat` tests and help us in building vignettes that show how to (and how NOT to)
use the package. By participating in this project you agree to abide by its terms.

>>>>

To install the developmental version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this developmental version is at <https://infer.netlify.com>.

@@

We welcome others helping us make this package as user friendly and efficient as possible. Please review
our [contributing](https://github.com/andrewpbray/infer/blob/develop/CONDUCT.md) and [conduct](CONDUCT.md) guidelines. Of particular interest is
helping us to write `testthat` tests and in building vignettes that show how to (and how NOT to)
use the package. By participating in this project you agree to abide by its terms.
